### 2019-05-24 7_conclusion.tex
Update conclusion.

Task Bench is a new approach for evaluating the performance
of parallel and distributed programming systems. We have seen that
systems vary by orders of magnitude in runtime overhead, as measured
by METG. Widely used systems in industry have METG measured in
seconds, reflecting the very coarse tasks and lack of need for strong
scaling performance in current workloads. At the other extreme,
traditional HPC systems have METG in the range of 10-100 \textmu{}s,
necessary for strong scaling to small task granularities, though we
have shown that METG also increases significantly for these systems
with the size of the cluster and the use offload accelerators. The newer
task-based systems, with METG in the range of 100 \textmu{}s to 1 ms
have performance sufficient for weak scaling many HPC workloads, but
more work is needed to strong scale the most demanding applications.

>>>>

Task Bench is a new approach for evaluating the performance of
parallel and distributed programming systems. By separating the
specification of a benchmark from implementations in various
programming systems, it is possible to explore a broad space of
application scenarios and to do so with a large number of programming
systems. Our experiments have enabled the following
insights:

\begin{itemize}

\item METG for current distributed programming systems varies by over
  5 orders of magnitude.  Clearly understanding the needed task
  granularity is an important consideration in choosing a programming
  system for a new application.

\item While some systems support task granularities as small as a few
  microseconds, this applies only to small CPU-based clusters. Adding
  accelerators or moving to clusters of hundreds of nodes raises the
  METG that any system can achieve by over an order of magnitude.

\item Systems that support asynchronous execution show benefits under
  load imbalanced workloads, or workloads with balanced computation
  and communication. However, these gains can be easily nullified by
  high baseline overheads.

\item Systems for large scale data analysis require very large tasks
  (in the tens of seconds) to scale beyond small numbers of nodes,
  reflecting the very coarse tasks and lack of need for strong scaling
  performance in current workloads.

\item The newer task-based systems have performance sufficient for
  weak scaling many HPC workloads, but more work is needed to strong
  scale the most demanding applications.

\end{itemize}
